\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-04 cc-condensed.tex
Fix typo. Remove a seal
consistency

% Canonicity / Consistency Condensed
\noindentparagraph{Consistency and Canonicity.}
Two of the most fundamental properties for dependent type theory are \textit{consistency} and \textit{canonicity}:
\begin{theorem}[Consistency]
  $\goodTerm{\cdot}{t}{\bot}$ is not derivable, i.e. $\bot$ is not inhabitted in the empty context
\end{theorem}
\begin{theorem}[Canonicity]
  if $\goodTerm{\cdot}{t}{\cB}$ then it is either $\goodTerm{\cdot}{t \equiv \true}{\cB}$ or $\goodTerm{\cdot}{t \equiv \false}{\cB}$
\end{theorem}
Consistency means our dependent type theory suffices as a logical system as not every proposition is trivially provable. Canonicity implies our dependent type theory sufficies as ``a computational foundation for mathematics''\footnote{See nlab explanation: \href{https://ncatlab.org/nlab/show/canonical+form}{Canonical Form}}. We can even argue that, if this canonicity theorem is proven in a computable meta-logic\footnote{QIIT does have computational content~\cite{altkap2016}}, 
then by Curry-Howard Correspondence, this theorem provides a big-step interpreter for closed term of boolean type.

>>>>

% Canonicity / Consistency Condensed
\noindentparagraph{Consistency and Canonicity.}
Two of the most fundamental properties for dependent type theory are \textit{consistency} and \textit{canonicity}.
\begin{theorem}[Consistency]
  The typing judgment $\goodTerm{\cdot}{t}{\bot}$ is not derivable for any term~$t$.
\end{theorem}
\begin{theorem}[Canonicity]
  If $\goodTerm{\cdot}{t}{\cB}$, then either $\goodTerm{\cdot}{t \equiv \true}{\cB}$ or $\goodTerm{\cdot}{t \equiv \false}{\cB}$.
\end{theorem}

Consistency says that the type $\bot$ is uninhabitable.
Thus, it is safe to use the type theory for logical reasoning, as not
every proposition is trivially provable.
Consistency is a consequence of a meta\-circular interpretation of all
the well-formedness rules, which, in particular, interprets $\bot$ in
\TT as an uninhabited type in the meta\-language.
The construction of this interpretation follows the standard model of
\citet{altkap2016}, extending it to handle linkages.
We refer the reader to a supplemental Agda file for the complete proof.

Canonicity implies our dependent type theory suffices as ``a computational foundation for mathematics''\footnote{See nlab explanation: \href{https://ncatlab.org/nlab/show/canonical+form}{Canonical Form}}. We can even argue that, if this canonicity theorem is proven in a computable meta-logic\footnote{QIIT does have computational content~\cite{altkap2016}},

\newpage

\ifShowOldWriting

then by Curry-Howard Correspondence, this theorem provides a big-step interpreter for closed term of boolean type.
